---
title: "BP: Data Cleaning"
author: Brenden Eum
date: February 14, 2023
output: 
  html_document: 
    theme: united
    toc: yes
    toc_float: yes
    toc_depth: 2
    number_sections: yes
    code_folding: hide
    df_print: default
---

# Preamble

Start fresh, set seed, load libraries, set directories.

```{r load, message=FALSE, warning=FALSE}

rm(list = ls())
seed = 1337
library(dplyr)      # pipeline %>%

datadir <- '../data' #data
figdir <- '../00 pilot/figures' #figures
outdir <- '../00 pilot/output' #output
tempdir <- '../00 pilot/temp' #temp folder

```


# Load Data

* Read the csv file with all the subject data. 
* Make a list of variables that you're interested in, and only keep those in the main data set.
* Only keep subjects that completed the task.

```{r}

variables_of_interest <- c(
  "Participant.Status", #       Make sure subjects completed the experiment
  "Participant.Private.ID", #   Unidentifiable subject ID number
  "trial", #                    Randomized numbering of trials (you'll need to overwrite this later)
  "block", #                    Randomized numbering of blocks
  "display", #                  Display name from Gorilla
  "Screen.Name", #              Screen name from Gorilla
  "Response", #                 Subject's response
  "Reaction.Time", #            Reaction time in ms
  "duration", #                 How long was the stimulus displayed for? (ms)
  "Correct", #                  Did subject's response match the correct answer (1=Y, 0=N)
  "ANSWER", #                   What was the correct answer?
  "stimulus", #                 Which stimulus was used? ("blue" or "red", followed by an ID number for the randomly generated stimulus)
  "sanity", #                   Was this a sanity check trial? (i.e. a trial where the outcome is easy to determine, say 80% red)
  "bias"  #                     What color is favored this block? (i.e. 60% of trials favor red)
)

data.raw <- read.csv(
  file = file.path(datadir, "pilotdata_exp_105297-v6_task-unu1.csv")
)

data.main <- data.raw[data.raw$Participant.Status=="complete", variables_of_interest]

```


# data.main Cleaning and Transformation

* Rename columns.
* Factorize.
* Drop NA.

```{r}

# Rename certain columns.

data.main <- data.main %>%
  rename(
    subject = "Participant.Private.ID",
    screen = "Screen.Name",         
    response = "Response",             
    rt = "Reaction.Time",      
    stimDur = "duration",
    correct = "Correct",            
    correctResponse = "ANSWER",
    sanity = "sanity",
    bias = "bias"
  )

# Factorize subject number.

data.main$subject <- data.main$subject %>%
  factor() %>%
  as.numeric() %>%
  factor()

# Create a mapping from subject, trial to stimulus duration.

rawStimDur <- data.main[data.main$display == "Trial" & data.main$screen == "Stimulus", c("subject", "trial", "rt")]
rawStimDur <- rawStimDur %>% rename(stimDur.raw = "rt")

# Prune data.main down to just the response screens.

data.main <- data.main[data.main$display == "Trial" & data.main$screen == "Response",]

# Add new trial numbers and blocks to data.main.

data.main <- data.main %>%
  group_by(subject) %>%
  mutate(
    trial = row_number()
  )
data.main[data.main$trial <= 100, "block"] <- 1
data.main[data.main$trial > 100 & data.main$trial <= 200, "block"] <- 2
data.main[data.main$trial > 200 & data.main$trial <= 300, "block"] <- 3
data.main[data.main$trial > 300 & data.main$trial <= 400, "block"] <- 4

# Round rt to nearest 1 ms.

data.main$rt <- data.main$rt %>% as.numeric() %>% round()

# Add raw stimulus durations for comparison... but will probably end up using "duration" variable since it's already rounded.

data.main$simDur.raw <- rawStimDur$stimDur.raw

# Change response and correctResponse to numeric (1 = Left, 0 = Right).

data.main$response <- ifelse(data.main$response=="left", 1, 0)
data.main$correctResponse <- ifelse(data.main$correctResponse=="left", 1, 0)


```


# data.main Quality Filter

* Drop if...
  * Did not complete experiment.
  * <90% accuracy in sanity checks.
  
```{r}

# Check if status == complete. Then drop the variable after.

dropped.statusIncomplete <- unique(data.main[data.main$Participant.Status!="complete", "subject"])
data.main <- data.main[data.main$Participant.Status=="complete", ]
data.main <- select(data.main,-"Participant.Status")

# Drop if <90% accuracy in sanity checks.

QC <- data.main[data.main$sanity==1,] %>%
  group_by(subject) %>%
  summarize(
    accuracy = mean(correct)
  )
dropped.QC <- unique(QC[QC$accuracy<.9, "subject"])
for (sub in dropped.QC$subject) {
  data.main <- data.main[data.main$subject != sub,]
}

```


# Save data.main

* Write data.main to a csv.

```{r}

write.csv(
  data.main, 
  file.path(outdir, "data.main.csv")
)

```