---
title: "BP: Analysis"
author: Brenden Eum
date: February 14, 2023
output: 
  html_document: 
    theme: united
    toc: yes
    toc_float: yes
    toc_depth: 2
    number_sections: yes
    code_folding: hide
    df_print: default
---


# Preamble

Start fresh, set seed, load libraries, set directories, and dictate whether you want analysis to occur quickly and verbose-ly.

```{r load, message=FALSE, warning=FALSE}

rm(list = ls())
seed = 1337
library(dplyr) #pipeline %>%
library(plotrix) #std.error
library(ggplot2) #plots... duh
library(grid) #combine plots
library(gridExtra) #more combining plots
library(ggsci) #I like the Futurama color palette <3
library(latex2exp) #for fancy math stuffs in the plots

rawdatadir <- '../data' # raw data
datadir <- '../00 pilot/clean_data' # clean data
figdir <- '../00 pilot/figures' # figure folder
tbldir <- '../00 pilot/tables' # figure folder
tempdir <- '../00 pilot/temp' # temp folder
textdir <- "../00 pilot/text" # text folder
final.figdir <- "../biased-priors-manuscript/figures"
final.txtdir <- "../biased-priors-manuscript/text-files"
final.tbldir <- "../biased-priors-manuscript/tables"

```


# Useful Functions

```{r}

# estimate and return the mode of a distribution (in this case, the posterior)
estimate_mode <- function(x) {
  d <- density(x)
  return( d$x[which.max(d$y)] )
}

# estimate 95 HDI
estimate_hdi <- function(x, conf=.95) {
  lb <- 0 + (1-conf)/2
  ub <- 1 - (1-conf)/2
  d <- quantile(x, probs = c(lb,ub), na.rm = F,
           names = TRUE)
  return(d)
}

```


# Plot Options

```{r}

linesize = 2
markersize = .1
ribbonalpha = 0.33
jitter_amt = 0.075
textsize <- 18
legtxtsize <- 18
plot_margins <- 1
legend_location <- "none"

col_title_size = 22
col_title_face = 'bold'

back_fill_e = 'lightcyan1'
back_fill_c = 'mistyrose1'
back_fill_j = 'lightcyan2'

plot_width = 8
plot_height = 8
final_plot_units = c('in')

colors <- c(
  "1" = "#00BFC4", #blue
  "0" = "#F8766D"  #red
)
colors_correct <- c(
  "1" = "darkgreen",  #correct
  "0" = "darkred"  #incorrect
)

ggplot <- function(...) ggplot2::ggplot(...) + 
  theme_bw() +
  #plot options
  theme(
    panel.grid.major=element_blank(), 
    panel.grid.minor=element_blank(),
    text=element_text(size=textsize),
    plot.margin=unit(c(plot_margins,plot_margins,plot_margins,plot_margins),"cm")
  ) +
  #legend options
  theme(
    legend.title = element_blank(),
    legend.position = legend_location,
    legend.justification = c(0, 1),
    legend.text = element_text(size = legtxtsize),
    legend.background = element_rect(fill = "transparent")
  ) +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) 
  

```


# Read-in Data

```{r}

data.main <- read.csv(file.path(datadir, "data.main.csv"))

```


# Results

## * Sanity Checks

### - Accuracy

```{r}

pdata.SanityCheckAcc <- data.main[data.main$sanity==1, ] %>%
  group_by(subject) %>%
  summarize(
    accuracy.sub = mean(correct)
  )

p.SanityCheckAcc <- ggplot(data=pdata.SanityCheckAcc, aes(x=accuracy.sub)) +
  annotate(
    "rect", 
    xmin = .85, xmax = .9, 
    ymin = 0, ymax = 15,
    alpha = .1, fill = "darkred") +
  geom_vline(
    xintercept = 0.90, 
    linetype = "dashed", 
    color = "darkred",
    alpha = .7,
    size = linesize
  ) +
  geom_density(
    color = "grey30",
    fill = "grey50",
    size = linesize
  ) +
  coord_cartesian(expand=F) +
  xlim(c(.85,1)) +
  ylim(c(0,NA)) +
  labs(
    x = "Accuracy",
    y = "Density"
  )

plot(p.SanityCheckAcc)

ggsave(
  file.path(figdir, "p.SanityCheckAcc.pdf"),
  plot = p.SanityCheckAcc
)
ggsave(
  file.path(final.figdir, "p.SanityCheckAcc.pdf"),
  plot = p.SanityCheckAcc
)

```

### - RT, by Correct

```{r}

pdata.SanityCheckRT <- data.main[data.main$sanity==1, ] %>%
  group_by(subject, correct) %>%
  summarize(
    rt.sub = mean(rt)
  )

pdata.SanityCheckRT$correct <- pdata.SanityCheckRT$correct %>%
  factor(
    levels = c(1,0)
  )

p.SanityCheckRT <- ggplot(pdata.SanityCheckRT, aes(x=correct, y=rt.sub, fill=correct)) +
  geom_boxplot(
    color = "grey55",
    size = linesize,
    outlier.alpha = 0
  ) +
  ylim(c(0,2000)) +
  labs(
    y = "Mean Response Time (ms)"
  ) +
  theme(
    axis.title.x=element_blank()
  ) +
  coord_cartesian(expand=T) +
  scale_color_manual(values = colors_correct) +
  scale_fill_manual(values = colors_correct)

plot(p.SanityCheckRT)

ggsave(
  file.path(figdir, "p.SanityCheckRT.pdf"),
  plot = p.SanityCheckRT
)
ggsave(
  file.path(final.figdir, "p.SanityCheckRT.pdf"),
  plot = p.SanityCheckRT
)

```


## * Basic Psychometrics

### - Accuracy

```{r}

pdata.Accuracy <- data.main[data.main$sanity==0, ] %>%
  group_by(subject, stimDur) %>%
  summarize(
    accuracy.sub = mean(correct)
  ) %>%
  group_by(stimDur) %>%
  summarize(
    accuracy.se = std.error(accuracy.sub),
    accuracy.mean = mean(accuracy.sub)
  )

p.Accuracy <- ggplot(data=pdata.Accuracy, aes(x=stimDur, y=accuracy.mean)) +
  geom_line(
    size = linesize
  ) +
  geom_ribbon(
    aes(
      ymin=accuracy.mean-accuracy.se,
      ymax=accuracy.mean+accuracy.se
    ),
    size=linesize,
    markersize=markersize,
    alpha = ribbonalpha
  ) +
  ylim(c(0,1)) +
  coord_cartesian(expand=T) +
  labs(
    x = "Stimulus Duration (ms)",
    y = "Accuracy"
  )

plot(p.Accuracy)

ggsave(
  file.path(figdir, "p.Accuracy.pdf"),
  plot = p.Accuracy
)
ggsave(
  file.path(final.figdir, "p.Accuracy.pdf"),
  plot = p.Accuracy
)

```

### - Accuracy, by Correct Color

```{r}

# PLOT

temp <- data.main[data.main$sanity==0, ] %>%
  group_by(subject, stimDur, correctResponse) %>%
  summarize(
    accuracy.sub = mean(correct)
  ) 

pdata.AccuracyByCorrectColor <- temp %>%
  group_by(stimDur, correctResponse) %>%
  summarize(
    accuracy.se = std.error(accuracy.sub),
    accuracy.mean = mean(accuracy.sub)
  )

pdata.AccuracyByCorrectColor$correctResponse <- pdata.AccuracyByCorrectColor$correctResponse %>% factor() 

p.AccuracyByCorrectColor <- 
  ggplot(data=pdata.AccuracyByCorrectColor, aes(x=stimDur, y=accuracy.mean, group=correctResponse)) +
  geom_line(
    aes(color=correctResponse),
    size = linesize
  ) +
  geom_ribbon(
    aes(ymin=accuracy.mean-accuracy.se, ymax=accuracy.mean+accuracy.se, fill=correctResponse),
    size=linesize,
    markersize=markersize,
    alpha = ribbonalpha
  ) +
  ylim(c(0,1)) +
  coord_cartesian(expand=T) +
  labs(
    x = "Stimulus Duration (ms)",
    y = "Accuracy"
  ) 
  

plot(p.AccuracyByCorrectColor)

ggsave(
  file.path(figdir, "p.AccuracyByCorrectColor.pdf"),
  plot = p.AccuracyByCorrectColor
)
ggsave(
  file.path(final.figdir, "p.AccuracyByCorrectColor.pdf"),
  plot = p.AccuracyByCorrectColor
)


# TEXT

ttest.pval <- c()
ind <- 1

for (stimulusDuration in unique(temp$stimDur)) {
  
  ttest.pval[ind] <- t.test(
    x = temp[temp$stimDur==stimulusDuration & temp$correctResponse==0, "accuracy.sub"],
    y = temp[temp$stimDur==stimulusDuration & temp$correctResponse==1, "accuracy.sub"],
    alternative = "two.sided"
  )$p.value
  ind <- ind + 1
  
}

mini <- min(ttest.pval) %>% round(2) %>% toString()
writeLines(
  mini, 
  file.path(final.txtdir, "accuracyByColor_min_pval.txt")
)

maxi <- max(ttest.pval) %>% round(2) %>% toString()
writeLines(
  maxi, 
  file.path(final.txtdir, "accuracyByColor_max_pval.txt")
)

```


### - RT

```{r}

pdata.RT <- data.main[data.main$sanity==0, ] %>%
  group_by(subject, stimDur) %>%
  summarize(
    rt.sub = mean(rt)
  ) %>%
  group_by(stimDur) %>%
  summarize(
    rt.se = std.error(rt.sub),
    rt.mean = mean(rt.sub)
  )

p.RT <- ggplot(pdata.RT, aes(x=stimDur, y=rt.mean)) +
  geom_line(
    size = linesize
  ) +
  geom_ribbon(
    aes(ymin=rt.mean-rt.se, ymax=rt.mean+rt.se),
    size=linesize,
    markersize=markersize,
    alpha = ribbonalpha
  ) +
  # options
  ylim(c(0,NA)) +
  coord_cartesian(expand=T) +
  labs(
    x = "Stimulus Duration (ms)",
    y = "Response Time (ms)"
  ) 

plot(p.RT)

ggsave(
  file.path(figdir, "p.RT.pdf"),
  plot = p.RT
)
ggsave(
  file.path(final.figdir, "p.RT.pdf"),
  plot = p.RT
)

```

### - RT, by Correct

```{r}

pdata.RTByCorrect <- data.main[data.main$sanity==0, ] %>%
  group_by(subject, stimDur, correct) %>%
  summarize(
    rt.sub = mean(rt)
  ) %>%
  group_by(stimDur, correct) %>%
  summarize(
    rt.se = std.error(rt.sub),
    rt.mean = mean(rt.sub)
  )

pdata.RTByCorrect$correct <- pdata.RTByCorrect$correct %>% factor()

p.RTByCorrect <- ggplot(pdata.RTByCorrect, aes(x=stimDur, y=rt.mean, group=correct)) +
  geom_line(
    aes(color=correct),
    size = linesize
  ) +
  geom_ribbon(
    aes(ymin=rt.mean-rt.se, ymax=rt.mean+rt.se, fill=correct),
    size=linesize,
    markersize=markersize,
    alpha = ribbonalpha
  ) +
  # options
  ylim(c(0,NA)) +
  coord_cartesian(expand=T) +
  labs(
    x = "Stimulus Duration (ms)",
    y = "Response Time (ms)"
  ) +
  scale_color_manual(values = colors_correct) +
  scale_fill_manual(values = colors_correct)

plot(p.RTByCorrect)

ggsave(
  file.path(figdir, "p.RTByCorrect.pdf"),
  plot = p.RTByCorrect
)
ggsave(
  file.path(final.figdir, "p.RTByCorrect.pdf"),
  plot = p.RTByCorrect
)

```


## * Choice wrt Stim Dur, by Correct and Bias

### - Bias: Red

```{r}

pdata.ChoiceRedBias <- data.main[data.main$bias=="red" & data.main$sanity==0, ] %>%
  group_by(subject, stimDur, correctResponse) %>%
  summarize(
    mean.response = mean(response)
  ) %>%
  group_by(stimDur, correctResponse) %>%
  summarize(
    y = mean(mean.response),
    se = std.error(mean.response)
  )

pdata.ChoiceRedBias$correctResponse <- pdata.ChoiceRedBias$correctResponse %>% factor() 

p.ChoiceRedBias <- ggplot(data=pdata.ChoiceRedBias, aes(x=stimDur, y=y, group=correctResponse)) +
  geom_hline(
    yintercept=.5, 
    color='grey'
  ) +
  geom_line(
    aes(color=correctResponse), 
    size=linesize,
    show.legend=F
  ) +
  geom_ribbon(
    aes(ymin=y-se, ymax=y+se, fill=correctResponse), 
    size=linesize, 
    alpha=ribbonalpha, 
    show.legend=F
  ) +
  labs(
    title = "Biased Red",
    y = "Pr(choose blue)",
    x = "Stimulus duration (ms)",
    color = "Stimulus"
  ) +
  coord_cartesian(
    #xlim = c(0,1000),
    ylim = c(0,1)
  ) +
  theme(
    legend.position = c(.1,.15)
  )

plot(p.ChoiceRedBias)

ggsave(
  file.path(figdir, "fig_ChoiceRedBias.pdf"),
  plot = p.ChoiceRedBias
)
ggsave(
  file.path(final.figdir, "fig_ChoiceRedBias.pdf"),
  plot = p.ChoiceRedBias
)

```


### - Bias: Blue

```{r}

pdata.ChoiceBlueBias <- data.main[data.main$bias=="blue" & data.main$sanity==0, ] %>%
  group_by(subject, stimDur, correctResponse) %>%
  summarize(
    mean.response = mean(response)
  ) %>%
  group_by(stimDur, correctResponse) %>%
  summarize(
    y = mean(mean.response),
    se = std.error(mean.response)
  )

pdata.ChoiceBlueBias$correctResponse <- pdata.ChoiceBlueBias$correctResponse %>% factor() 

p.ChoiceBlueBias <- ggplot(data=pdata.ChoiceBlueBias, aes(x=stimDur, y=y, group=correctResponse)) +
  geom_hline(
    yintercept=.5, 
    color='grey'
  ) +
  geom_line(
    aes(color=correctResponse), 
    size=linesize,
    show.legend=F
  ) +
  geom_ribbon(
    aes(ymin=y-se, ymax=y+se, fill=correctResponse), 
    size=linesize, 
    alpha=ribbonalpha, 
    show.legend=F
  ) +
  labs(
    title = "Biased Blue",
    y = "Pr(choose blue)",
    x = "Stimulus duration (ms)",
    color = "Stimulus"
  ) +
  coord_cartesian(
    #xlim = c(0,1000),
    ylim = c(0,1)
  ) +
  theme(
    legend.position = c(.1,.15)
  )

plot(p.ChoiceBlueBias)

ggsave(
  file.path(figdir, "fig_ChoiceBlueBias.pdf"),
  plot = p.ChoiceBlueBias
)
ggsave(
  file.path(final.figdir, "fig_ChoiceBlueBias.pdf"),
  plot = p.ChoiceBlueBias
)

```

## * Choice Var. wrt Stim Dur. by Correct and Bias

### - All (**FIX?**)

```{r}

pdata.ChoiceVarAll <- data.main[data.main$sanity==0, ] %>%
  group_by(subject, stimDur, correct) %>%
  summarize(
    var.response = var(response)
  ) %>%
  group_by(stimDur, correct) %>%
  summarize(
    y = mean(var.response),
    se = std.error(var.response)
  )

pdata.ChoiceVarAll$correct <- pdata.ChoiceVarAll$correct %>% factor()

p.ChoiceVarAll <- ggplot(data=pdata.ChoiceVarAll, aes(x=stimDur, y=y, group=correct)) +
  geom_line(
    aes(color=correct), 
    size=linesize,
    show.legend=F
  ) +
  geom_ribbon(
    aes(ymin=y-se, ymax=y+se, fill=correct), 
    size=linesize, 
    alpha=ribbonalpha, 
    show.legend=F
  ) +
  labs(
    y = "Variance(choose blue)",
    x = "Stimulus duration (ms)"
  ) +
  theme(
    legend.position = c(.1,.15)
  )

plot(p.ChoiceVarAll)

ggsave(
  file.path(figdir, "fig_ChoiceVarAll.pdf"),
  plot = p.ChoiceVarAll
)
ggsave(
  file.path(final.figdir, "fig_ChoiceVarAll.pdf"),
  plot = p.ChoiceVarAll
)

```

### - Bias: Red

```{r}

pdata.ChoiceVarRedBias <- data.main[data.main$bias=="red" & data.main$sanity==0, ] %>%
  group_by(subject, stimDur, correctResponse) %>%
  summarize(
    var.response = var(response)
  ) %>%
  group_by(stimDur, correctResponse) %>%
  summarize(
    y = mean(var.response),
    se = std.error(var.response)
  )

pdata.ChoiceVarRedBias$correctResponse <- pdata.ChoiceVarRedBias$correctResponse %>% factor() 

p.ChoiceVarRedBias <- ggplot(data=pdata.ChoiceVarRedBias, aes(x=stimDur, y=y, group=correctResponse)) +
  geom_line(
    aes(color=correctResponse), 
    size=linesize,
    show.legend=F
  ) +
  geom_ribbon(
    aes(ymin=y-se, ymax=y+se, fill=correctResponse), 
    size=linesize, 
    alpha=ribbonalpha, 
    show.legend=F
  ) +
  labs(
    title = "Biased Red",
    y = "Variance(choose blue)",
    x = "Stimulus duration (ms)",
    color = "Stimulus"
  ) +
  theme(
    legend.position = c(.1,.15)
  )

plot(p.ChoiceVarRedBias)

ggsave(
  file.path(figdir, "fig_ChoiceVarRedBias.pdf"),
  plot = p.ChoiceVarRedBias
)
ggsave(
  file.path(final.figdir, "fig_ChoiceVarRedBias.pdf"),
  plot = p.ChoiceVarRedBias
)

```

### - Bias: Blue

```{r}

pdata.ChoiceVarBlueBias <- data.main[data.main$bias=="blue" & data.main$sanity==0, ] %>%
  group_by(subject, stimDur, correctResponse) %>%
  summarize(
    var.response = var(response)
  ) %>%
  group_by(stimDur, correctResponse) %>%
  summarize(
    y = mean(var.response),
    se = std.error(var.response)
  )

pdata.ChoiceVarBlueBias$correctResponse <- pdata.ChoiceVarBlueBias$correctResponse %>% factor() 

p.ChoiceVarBlueBias <- ggplot(data=pdata.ChoiceVarBlueBias, aes(x=stimDur, y=y, group=correctResponse)) +
  geom_line(
    aes(color=correctResponse), 
    size=linesize,
    show.legend=F
  ) +
  geom_ribbon(
    aes(ymin=y-se, ymax=y+se, fill=correctResponse), 
    size=linesize, 
    alpha=ribbonalpha, 
    show.legend=F
  ) +
  labs(
    title = "Biased Blue",
    y = "Variance(choose blue)",
    x = "Stimulus duration (ms)",
    color = "Stimulus"
  ) +
  theme(
    legend.position = c(.1,.15)
  )

plot(p.ChoiceVarBlueBias)

ggsave(
  file.path(figdir, "fig_ChoiceVarBlueBias.pdf"),
  plot = p.ChoiceVarBlueBias
)
ggsave(
  file.path(final.figdir, "fig_ChoiceVarBlueBias.pdf"),
  plot = p.ChoiceVarBlueBias
)

```

